Fluent statistical computing interfaces for biological data analysis

### 2020-07-27 Rmd/03-fluentGenomics.Rmd
refactor and tidy up scripts for chapter 3

```{r tximeta-run, echo = TRUE}
```
<!-- should we describe the data structure in more detail, or use a figure -->

@@

Similarly, we can then combine the `boot_genes` _GRanges_, with the DE
_GRanges_ object. As the resample column was not present on the DE *GRanges*
object, this is given a missing value which we recode to a 0 using `mutate()`

@@

We are now ready to compute overlaps between RNA-seq genes (our DE set and
bootstrap sets) and the ATAC-seq peaks. In **plyranges**, overlaps are defined as
joins between two *GRanges* objects: a _left_ and a _right_ *GRanges* object.
In an overlap join, a match is any range on the _left_ *GRanges* that is
overlapped by the _right_ *GRanges*. One powerful aspect of the overlap joins
is that the result maintains all (metadata) columns from each of the _left_ and
_right_ ranges which makes downstream summaries easy to compute.

@@

There are several further steps that would be interesting to perform in this
analysis; for example, we could modify window size around the TSS to see how it
affects enrichment, and vary the FDR cut-offs for both the DE gene and DA peak
sets. We could also have computed variance in addition to the mean of the
bootstrap set, and so drawn an interval around the enrichment line.

>>>>

```{r tximeta-run, echo = TRUE}
```

@@

Similarly, we can then combine the `subsamp_genes` _GRanges_, with the DE
_GRanges_ object. As the resample column was not present on the DE *GRanges*
object, this is given a missing value which we recode to a 0 using `mutate()`

@@

We are now ready to compute overlaps between RNA-seq genes (our DE set and
resampled sets) and the ATAC-seq peaks. In **plyranges**, overlaps are defined as
joins between two *GRanges* objects: a _left_ and a _right_ *GRanges* object.
In an overlap join, a match is any range on the _left_ *GRanges* that is
overlapped by the _right_ *GRanges*. One powerful aspect of the overlap joins
is that the result maintains all (metadata) columns from each of the _left_ and
_right_ ranges which makes downstream summaries easy to compute.

@@

There are several further steps that would be interesting to perform in this
analysis; for example, we could modify window size around the TSS to see how it
affects enrichment, and vary the FDR cut-offs for both the DE gene and DA peak
sets. We could also have computed variance in addition to the mean of the
resampled set, and so drawn an interval around the enrichment line.
